---
title: "Replication 2"
author: "John LaVelle"
date: "2/17/2019"
output: 
  pdf_document:
    latex_engine: xelatex
  citation_package: natbib
  bibliography: bibliography.bib
    
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment=NA )
```

```{r, include=FALSE}

library(janitor)
library(xtable)
library(RItools)
library(ri)
library(RColorBrewer)
library(gt)
library(dplyr)
library(tidyverse)


# elminates dirty line before xtable
options(xtable.comment = FALSE)



# Loading in the data using read_csv instead of read.csv
pnas_data   <- read.csv("dataverse_files/pnas_dat/pnas_data.csv")
t1_data     <- read.csv("dataverse_files/pnas_dat/t1_data.csv")
prime_data  <- read.csv("dataverse_files/pnas_dat/prime_data.csv")

```

Always a good idea to include an abstract.

# Table 1
```{r, main}
###inference
repeats = c("numberim","Remain","Englishlan")
x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")
covariates = c('line.x')

###treated first
final.mat = matrix(nrow = 0, ncol = 8)

subsets = c('all','no.car')

for(subset in subsets){

  # make column of appropriate length
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	
	# choose data fo the analysis
	if(subset == 'all'){
		dat.subset = pnas_data
		}
	if(subset ==  'no.car'){
		dat.subset = pnas_data[pnas_data$habits != 1,]
		}

		
	z.variable = 'treatment'
	
	# compute summary statistics
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
		
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		y.mean = mean(dat.use$y.new,na.rm = T)
		y.treat = mean(dat.use$y.new[dat.use$treatment==1],na.rm = T)
	
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
				
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		}
	final.mat = rbind(final.mat,out.mat)
	}

final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean')

final.mat.main = final.mat ##final.mat for output creation later

gt(final.mat.main)

# definitely would be good to format this table a bit more (column headers, rounding, footnotes, etc) 
# and see if you make it fit a little more nicely on the page. 
# in its current state it appears a bit messy
```

\newpage
## Table 2

Here we convert Table 2 into a graphical representation, comparing the means of the different variables. Each difference is the difference between the treatment and control groups. (Treatment - Control)

```{r, results="asis"}

# Table 2

# from the documentation, xBalance does the following:

# Given covariates, a treatment variable, and a stratifying factor, 
# calculates standardized mean differences along each covariate, 
# with and without the stratification and tests for conditional 
# independence of the treatment variable and the covariates within strata.

# in effect, it seems like it groups things based on stratifying factors and finds statistics surrounding them 
balance_table <- xBalance(fmla = treatment ~ liberal+republican+obama.disapprove+ride.everyday+voted.2010+romney.voter+Hispanics.x+age+residency.new+hispanic.new+college+income.new+male+white, 
                          data = pnas_data, 
                          report = c("std.diffs","z.scores","adj.means","chisquare.test"), 
                          strata = factor(pnas_data$station))

balance_xtable <- xtable(balance_table$results[,1:4,], 
                         label="Table 2. Covariate balance across treatment conditions", 
                         digits=2,
                         align = "lrrrr")

labels = c("Liberal", "Republican", "Obama disapprove", 
                  "Ride MBTA every day", "Voted 2010", "Romney voter", "Hispanic threat", 
                   "Age", "Residency year", "College", "Male",  
                   "Hispanic", "White", "Income", "n") 

balance_xtable <- mutate(balance_xtable, labels = labels[row_number()])


# code to generate graphical representation of this data 
# starting portion of this code was taken from:
# https://stackoverflow.com/questions/42704821/error-when-trying-to-set-scale-x-discrete-and-scale-y-discrete

ggplot(balance_xtable, aes(y=labels,x=`std.diff`)) + geom_point() +
theme(axis.text.x  = element_text(angle=90, vjust=0.5, size=10), 
      axis.text.y  = element_text(angle=0, vjust=0.5, size=10)) +
scale_x_continuous(position = "top") + 
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
labs(x = "Standard Differences in Means", y = "variable")


```
\newpage

For future extensions I would recommend talking a little more about your extension. Why did you choose to do what you did? What does it show? What are the advantages/disadvantages of this method over the one's used by the author? How does it help you or the reader better understand the results presented in the original paper? The extension is your opportunity to show us what you've learned in the class and how to apply it, so tell us what you're thinking.

Making comments/notes about what we talked about in class where the code gets complex might be helpful moving forward.

The figure and the original table 2 that was supposed to be replicated is missing in the PDF output and code. You may have had it in earlier versions before the extension, so no worries, but in the future make sure you keep all the original parts of the replication and then include your extension at the end or in a separate file, whichever you prefer.

## References

Enos, Ryan D. 2014. “Causal Effect of Intergroup Contact on Exclusionary Attitudes.” Proceedings of the National Academy of Sciences 111 (10). National Acad Sciences.

———. 2017. “Replication Data for: The Causal Effect of Intergroup Contact on Exclusionary Attitudes.” Harvard Dataverse. doi:10.7910/DVN/DOP4UB.

some code taken from: https://stackoverflow.com/questions/42704821/error-when-trying-to-set-scale-x-discrete-and-scale-y-discrete 
