---
title: "Replication 2"
author: "John LaVelle"
date: "2/17/2019"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment=NA )
```

Purpose of this first week's work:

"We spend two weeks on each replication exercise. In the first week, you should replicate the published work. This is mainly an exercise in getting [the preexisting] code to run. But you should also add lots of comments. How might the code be improved? Why have they made the choices they made? What other approaches might be worth trying? What don’t you understand?"

\newpage
```{r, include=FALSE}

library(janitor)
library(xtable)
library(RItools)
library(ri)
library(RColorBrewer)
library(gt)
library(dplyr)
library(tidyverse)


# elminates dirty line before xtable
options(xtable.comment = FALSE)



# Loading in the data using read_csv instead of read.csv
pnas_data   <- read.csv("dataverse_files/pnas_dat/pnas_data.csv")
t1_data     <- read.csv("dataverse_files/pnas_dat/t1_data.csv")
prime_data  <- read.csv("dataverse_files/pnas_dat/prime_data.csv")
confed_data <- read.csv("dataverse_files/pnas_dat/confederate_face_data.csv")
hisp_data   <- read.csv("dataverse_files/pnas_dat/hispanic_face_data.csv")
white_data  <- read.csv("dataverse_files/pnas_dat/white_face_data.csv")


```


```{r, main, include=FALSE}
# originally taken from main_results.r 

###inference
repeats = c("numberim","Remain","Englishlan")
x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")
covariates = c('line.x')

###treated first
final.mat = matrix(nrow = 0, ncol = 8)

subsets = c('all','no.car')

for(subset in subsets){

  # make column of appropriate length
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	
	# choose data fo the analysis
	if(subset == 'all'){
		dat.subset = pnas_data
		}
	if(subset ==  'no.car'){
		dat.subset = pnas_data[pnas_data$habits != 1,]
		}

		
	z.variable = 'treatment'
	
	# compute summary statistics
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
		
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		y.mean = mean(dat.use$y.new,na.rm = T)
		y.treat = mean(dat.use$y.new[dat.use$treatment==1],na.rm = T)
	
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
				
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		}
	final.mat = rbind(final.mat,out.mat)
	}

final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean')

final.mat.main = final.mat ##final.mat for output creation later


```

```{r subset_interference, include=FALSE, cache=TRUE}
# taken from subset_inference.r

# looks like this code breaks the data up by political group, and then analyzes each subgroup

repeats = c("numberim","Remain","Englishlan")

x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")
covariates = c('line.x')
var.names = c('Number of immigrants be increased?','Children of undocumented be allowed to stay?','English as official language?')

	
##dose response estimates comparison
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('ta','tb')

# compute summary statistics
for(subset in subsets){
  
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'ta'){
		dat.subset = pnas_data[pnas_data$t.time %in% c('t2a','t4a'),]
		}
	if(subset == 'tb'){
		dat.subset = pnas_data[pnas_data$t.time %in% c('t2b','t4b'),]
		}
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
	
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
				
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
	
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		}
		final.mat = rbind(final.mat,out.mat)
	}
final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')

final.mat.dose = final.mat ##mat for creating graph later
	
##ideology comparison
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('liberals.only','moderates.only','conservatives.only')

for(subset in subsets){ 

  # segment the data into groups
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'liberals.only'){
		dat.subset = pnas_data[pnas_data$ideology.x %in% c(1,2),]
		}
	if(subset == 'conservatives.only'){
		dat.subset = pnas_data[pnas_data$ideology.x %in% c(4,5),]
		}
	if(subset == 'moderates.only'){
		dat.subset = pnas_data[pnas_data$ideology.x == 3,]
		}
	z.variable = 'treatment'
	
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		# get summary stats
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)

		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		
		}
	final.mat = rbind(final.mat,out.mat)
	}
final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')

final.mat.ideology = final.mat ##for graph later


##friends comparison
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('low.friends','high.friends','middle.friends')


for(subset in subsets){ 

	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'low.friends'){
		dat.subset = pnas_data[pnas_data$Friends.x == 0,]
		}
	if(subset == 'high.friends'){
		dat.subset = pnas_data[pnas_data$Friends.x >= 5,]
		}
	if(subset == 'middle.friends'){
		dat.subset = pnas_data[pnas_data$Friends.x > 0 & pnas_data$Friends.x < 5,]
		}
	
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
			
	
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		
		}
	final.mat = rbind(final.mat,out.mat)
	}
	final.mat = as.data.frame(final.mat)
	colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')

		final.mat.friends = final.mat ##for graph
	


#######income subsets
subsets = c('low.income','middle.income', 'high.income')
final.mat = matrix(nrow = 0, ncol = 8)
for(subset in subsets){ 

	out.mat = matrix(nrow = length(repeats), ncol = 8)
	
	if(subset == 'low.income'){
		dat.subset = pnas_data[pnas_data$income.new < 105000,]
		}
	if(subset == 'middle.income'){
		dat.subset = pnas_data[pnas_data$income.new >= 105000 & pnas_data$income.new <= 135000,]
		}
	if(subset == 'high.income'){
		dat.subset = pnas_data[pnas_data$income.new > 135000,]
		}
	
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
				
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)

		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		
		}
	final.mat = rbind(final.mat,out.mat)
	}
final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')

final.mat.income = final.mat  ##for later




```

```{r, primetest, cache=TRUE, include=FALSE}
# taken from primetest.r

##primetest.r [ORIGINALLY]
###use randomization inference to look for changes in responses induced by experiment in subsets by covariates.

#####recodes
####race variable
prime_data$non.white = ifelse(prime_data$race_4 == 1, 1,0)
prime_data$non.white[is.na(prime_data$non.white)==T] = 0
prime_data$residency.new[prime_data$residency == 1] = 1
prime_data$residency.new[prime_data$residency == 2] = 3.5
prime_data$residency.new[prime_data$residency == 3] = 7.5
prime_data$residency.new[prime_data$residency == 4] = 12.5
prime_data$residency.new[prime_data$residency == 5] = mean(prime_data$age, na.rm = T)-15
prime_data$residency.new[prime_data$residency == 6] = mean(prime_data$age, na.rm = T)

#####recodes
###English language is reverse coded from other variables:
prime_data$Englishlan.x = recode(prime_data$Englishlan.x, 
                                 "5" = "1", "4" = "2", "2" = "4", "1" = "5")
prime_data$Englishlan.y = recode(prime_data$Englishlan.y, 
                                 "5" = "1", "4" = "2", "2" = "4", "1" = "5")

###gender recode
prime_data$male = ifelse(prime_data$gender == 1, 1, 0)

###inference
repeats = c("numberim","Remain","Englishlan")

x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")

covariates = c('line')
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('all.prime')

for(subset in subsets){ ##b.only, complier, and non-compler subsets
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	dat.subset = prime_data
		
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
			
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable])
		probs = genprobexact(Z = dat.use[,z.variable])
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
	
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		}
		final.mat = rbind(final.mat,out.mat)
		}
	final.mat = as.data.frame(final.mat)
	colnames(final.mat) = c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean')
	
	final.mat.prime = final.mat ##mat for creating output later

	
```

Table 1



```{r, results="asis"}
# Table 1

#output_create.r
	
# ####create output
 output.vars = c('numberim','Remain','Englishlan')
 var.names = c('Number of immigrants be increased?','Children of undocumented be allowed to stay?','English as official language?')

 
 ##main results
 ##cumalative results output
 final.mat.use = rbind(final.mat.main,final.mat.prime)

 final.mat.use$greater.p.value = as.numeric(as.character(final.mat.use$greater.p.value))
 final.mat.use$lesser.p.value = as.numeric(as.character(final.mat.use$lesser.p.value))
 final.mat.use$ate = as.numeric(as.character(final.mat.use$ate))
 final.mat.use$x.mean = as.numeric(as.character(final.mat.use$x.mean))
 final.mat.use$x.sd = as.numeric(as.character(final.mat.use$x.sd))
 final.mat.use$N = as.numeric(as.character(final.mat.use$N))
 final.mat.use$p.value = final.mat.use$greater.p.value

 final.mat.redact = final.mat.use[,c('variable','subset','ate','p.value','x.mean','x.sd','N')]
 final.mat.redact[,c('ate','p.value','x.mean','x.sd')] = round(final.mat.redact[,c('ate','p.value','x.mean','x.sd')],3)

 final.mat.redact$ate.new = paste(final.mat.redact$ate,' (',final.mat.redact$p.value,')',sep='')
 final.mat.redact$x.mean.new = paste(final.mat.redact$x.mean,' (',final.mat.redact$x.sd,')',sep='')

 out.mat.a = final.mat.redact[final.mat.redact$subset == 'all'&final.mat.redact$variable %in% output.vars,]

 out.mat.a = final.mat.redact[final.mat.redact$subset == 'all'&final.mat.redact$variable %in% output.vars,c('ate.new')]	
 out.mat.c = final.mat.redact[final.mat.redact$subset == 'no.car'&final.mat.redact$variable %in% output.vars,c('ate.new')]
 out.mat.x = final.mat.redact[final.mat.redact$subset == 'all'&final.mat.redact$variable %in% output.vars,c('x.mean.new')]
 Ns = c('N',max(final.mat.redact$N[final.mat.redact$subset=='all']),
	max(final.mat.redact$N[final.mat.redact$subset=='no.car']),
	max(final.mat.redact$N[final.mat.redact$subset=='all'])
	)

 h1 = c('',paste('(',1:3,')',sep = ''))
 h2 = c('','all respondents','waits on platform','all respondents')
 h3 = c('question','ATE (p)','CATE (p)','T1 levels (sd)')
 hs = rbind(h1,h2,h3)
 row.names(hs) = NULL
	
 out.mat = cbind(out.mat.a,cbind(out.mat.c,out.mat.x))
 out.mat = cbind(var.names,out.mat)
 out.mat = rbind(out.mat,Ns)
 
 out.mat = rbind(hs,out.mat)
 
 out.table = xtable(out.mat, digits = 3)

 gt(out.table)



```
\newpage

Figure 2

Description from the text: 

Time effects. ATE and 95% confidence intervals for 3-d treatment (solid circle) and 10-d treatment (open circle). P values from top to bottom generated from a two-tailed test against the Null Hypothesis of no difference in effect between the 3-d and 10-d treatments are P = 0.195, 0.094, and 0.305. n = 55 for 3-d dose and 54 for 10-d dose. Confidence intervals are constructed by drawing the 2.5% and 97.5% quantiles from the randomization distribution.

```{r, results="asis"}
# Figure 2

# taken from outgraphic_single_pnas.r

# note that this is just one of these little graphs that the replication code provides. 
# The others are not in the paper and are thus omitted from my report.


# graph presets, for formatting the graph.

os = .4
line.os = .015
y.point = .75
ylims = c(0,1.1)
xlims = c(-.35,.35)
points.cex = 4
lab.cex = 1.5
line.lwd = 4.5
axis.cex = 1.25

colors = brewer.pal(3,'Paired')[1:2] ##colors for pairs used in plots below

####dose graph

# par is like parameters, looks like we are setting something 
# to do with alignment on the page with these, found out by trial and error
par(mfrow = c(3,1)) 
par(mar = c(5,0,1,0))
par(bty = 'n')

	
##dose response graph
out.mat = final.mat.dose[,c('variable','subset','ate','quantile.lower','quantile.upper')]
out.mat$ate = as.numeric(as.character(out.mat$ate))
out.mat$quantile.lower = as.numeric(as.character(out.mat$quantile.lower))
out.mat$quantile.upper = as.numeric(as.character(out.mat$quantile.upper))

out.mat.ta = out.mat[out.mat$subset == 'ta'&out.mat$variable %in% output.vars,]
out.mat.tb = out.mat[out.mat$subset == 'tb'&out.mat$variable %in% output.vars,]

# actually graphing the data
for(i in 1:length(var.names)){
	plot(x  = out.mat.ta$ate[i], y = y.point, 
		xlim = xlims,
		ylim = ylims,
		ylab = '',
		xlab = var.names[i],
		yaxt = 'n',
		type = 'n',
		cex.lab = lab.cex,
		cex.axis = axis.cex)
	lines(x = c(out.mat.ta$quantile.lower[i],out.mat.ta$ate[i]-line.os), 
			y = c(y.point,y.point),
			lty = 1,
			col = colors[1],
			lwd = line.lwd)
	lines(x = c(out.mat.ta$ate[i]+line.os,out.mat.ta$quantile.upper[i]), 
			y = c(y.point,y.point),
			lty = 1,
			col = colors[1],
			lwd = line.lwd)
	lines(x = c(out.mat.tb$quantile.lower[i],out.mat.tb$ate[i]-line.os), 
			y = c(y.point-os,y.point-os),
			lty = 1,
			col = colors[2],
			lwd = line.lwd)
	lines(x = c(out.mat.tb$ate[i]+line.os,out.mat.tb$quantile.upper[i]), 
			y = c(y.point-os,y.point-os),
			lty = 1,
			col = colors[2],
			lwd = line.lwd)

	points(x  = out.mat.ta$ate[i], y = y.point,
		pch = 19,
		cex = points.cex,
		col = colors[1])
	points(x  = out.mat.tb$ate[i], y = y.point - os,
		pch = 1,
		cex = points.cex,
		col = colors[2])
}


```


\newpage
Table 2


```{r, results="asis"}

# Table 2


# balance_check.r




# from the documentation, xBalance does the following:

# Given covariates, a treatment variable, and a stratifying factor, 
# calculates standardized mean differences along each covariate, 
# with and without the stratification and tests for conditional 
# independence of the treatment variable and the covariates within strata.

# in effect, it seems like it groups things based on stratifying factors and finds statistics surrounding them 
balance_table <- xBalance(fmla = treatment ~ liberal+republican+obama.disapprove+ride.everyday+voted.2010+romney.voter+Hispanics.x+age+residency.new+hispanic.new+college+income.new+male+white, 
                          data = pnas_data, 
                          report = c("std.diffs","z.scores","adj.means","chisquare.test"), 
                          strata = factor(pnas_data$station))

balance_xtable <- xtable(balance_table$results[,1:4,], 
                         label="Table 2. Covariate balance across treatment conditions", 
                         digits=2,
                         align = "lrrrr")

# shoutout to Helen for this code, pretty cool when 
select(balance_xtable, 'treatment=0', 'treatment=1', std.diff, z) %>%  
  gt(rownames_to_stub = TRUE )

```

Table 3 is not completed because the data and the information are not included in the link above.
